Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-06-28 paper/Draft.tex
almost finished test results section.need a short summary.

\begin{abstract}
	Surveys on density forecasts of macroeconomic variable that are not available until recent dacade provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion not only in mean forecast but also in uncertainty about future inflation across economists and households. Second,  utilizing the panel data of individual uncertainty, I provide additional test results that reject the null hypothesis of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theoreis of expectation rigidity, but in the same time bears the evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific regidity using uncertainty as the next step of analysis.

@@

\begin{eqnarray}\label{VarREEq}
\bar \sigma^{*2}_{t+h|t+k} = \sum^{h-k}_{s=1}\rho^{2s} \sigma^2_{\omega}
\end{eqnarray}

@@

$$\sigma^2_{i,t|t-\tau}= \sum^{h+\tau}_{s=1}\rho^{2s} \sigma^2_{\omega}$$

@@

\begin{eqnarray}
\begin{aligned}
\bar \sigma^2_{t+h|t} & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who non-updater until }t-\tau} \underbrace{\sigma^2_{t+h|t-\tau}}_{\text{ uncertainty of most recent update at }t-\tau} \\
& = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
\end{aligned}
\end{eqnarray}

@@

\begin{eqnarray}\label{VarSEEq}
\begin{aligned}
\bar \sigma^2_{t+h|t+1} - \bar \sigma^2_{t+h|t} = (1-\lambda)(
\bar \sigma^2_{t+h|t} - \bar \sigma^2_{t+h|t-1}) -\lambda \rho^{2h} \sigma^2 
\end{aligned}
\end{eqnarray}

@@

Persistent disagreements in expectations has been used as an important stylized evidence against the null of identical expectation assumption embedded in FIRE, for instance, \citet{mankiw2003disagreement}. A similar fact checking can be done with respect to individual uncertaintiy. FIRE predicts individual share equal degree of uncertainty as  seen in Equation \ref{VarREEq}. In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEEq}). NI allows for possibility of homogeneity in uncertainty only under stringent condition of the equal precesion of signals and the same prior of uncertainty (Equation \ref{VarNIEq}). Therefore, precense of dispersion of uncertainty across agents can be read against FIRE.

@@

FE-based tests results are prensented in Table \ref{NullTestTable}. Individual level data are used thanks to the panel structure of both surveys. But since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE. Also,the regresions are adjusted corresponding to the quarterly and monthly frequency of SPF and SCE. Since these regressions are based on 1-year inflations in overlapping periods, white standard error is computed for hypothesis testing.

@@

The second batch of tests in Table \ref{RevEfficency} focus on testing forecasting efficiency using revisions of mean forecasts and uncertainty, as referred as Revision-based test.

In plain words, it checks if the revision from 1-year-ahead forecast to nowcast of current-year inflation is efficient by two criteria. (1) Forecast revision does not depend on past information, including the past revisions of forecast. (2) Drop in uncertainy are not serially correlated.

 \citet{fuhrer2018intrinsic}'s test for mean forecast revision takes the following form(using 1 period revision as an exampl).

@@

$\beta =0$ according to FIRE, because rational forecast revision only responds to newly realized shocks thus it is note predictable by past revisions.\footnote{Adding $y_{t+1|t}$ to both sides of Equation \ref{RevEffMeanTest} gives an equivalent null hypothesis used by \citet{fuhrer2018instrinsic}: coefficient of regression of $y_{t+1|t+1}$ on  $y_{t+1|t}$ is $1-\beta=1$. } Since we have four vintages of the forecasts from SPF, we can check if the revision in nowcasting are serially correlated with 1-year-ahead forecats in previous three quarters.

-----------------------------

@@

A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future. Table \ref{WeakRevEfficiency} present the results.

Weak efficiency tests use change in forecast and uncertainty instead of revisions. This is not a direct test of the null of FIRE as we have discussed that the rigidity models do not have direct testable predictions about the change in forecast and uncertainty with fixed forecast horizon. But in the same time, the auto regression features do speak to the persistence of the forecasts over the time horizon. In particular, if the individual forecasts and their uncertainty turn out to be persisent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.

@@

In Figure \ref{Inflationshocks}, all four shocks plus the unexplained component of inflation are plotted in quarterly between 1985-2019. All shocks are normalized by its respective sample standard deviations.

@@

The primary focus of this paper is the behavior of uncertainty. Its responses to the absolute value of various shocks is presented in the bottom of the panel. Since  average uncertainty do not directly depend on the realizations and sizes of the shocks in various models, as shown in Equation \ref{VarREEq}  Equation \ref{VarSEEq}, and Equation \ref{VarNIEq}, the response of uncertainty cannot be used as a screening device of  FIRE and rigidity models. Instead, it should be taken as a basic consistency check of different theories with respect to the behavior of uncertainty.

>>>>

\begin{abstract}
	Surveys on density forecasts of macroeconomic variable that are not available until recent dacade provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households. Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theoreis of expectation rigidity and points to evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific regidity using uncertainty as the next step of analysis.

@@

\begin{eqnarray}\label{VarREPop}
\bar \sigma^{*2}_{t+h|t+k} = \sum^{h-k}_{s=1}\rho^{2s} \sigma^2_{\omega}
\end{eqnarray}

@@

\begin{eqnarray}\label{VarSEInd}
	\sigma^2_{i,t|t-\tau}= \sum^{h+\tau}_{s=1}\rho^{2s} \sigma^2_{\omega}
\end{eqnarray}

@@

\begin{eqnarray}\label{VarSEPop}
\begin{aligned}
\bar \sigma^2_{t+h|t} & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who non-updater until }t-\tau} \underbrace{\sigma^2_{t+h|t-\tau}}_{\text{ uncertainty of most recent update at }t-\tau} \\
& = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
\end{aligned}
\end{eqnarray}

@@

\begin{eqnarray}\label{VarSERv}
\begin{aligned}
\bar \sigma^2_{t+h|t+1} - \bar \sigma^2_{t+h|t} = (1-\lambda)(
\bar \sigma^2_{t+h|t} - \bar \sigma^2_{t+h|t-1}) -\lambda \rho^{2h} \sigma^2 
\end{aligned}
\end{eqnarray}

@@

Persistent disagreements in expectations has been used as an important stylized evidence against the null of identical expectation assumption embedded in FIRE, for instance, \citet{mankiw2003disagreement}. A similar fact checking can be done with respect to individual uncertaintiy. FIRE predicts individual share equal degree of uncertainty as  seen in Equation \ref{VarREInd}. In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEInd}). NI allows for possibility of homogeneity in uncertainty only under stringent condition of the equal precesion of signals and the same prior of uncertainty (Equation \ref{VarNIEq}). Therefore, precense of dispersion of uncertainty across agents can be read against FIRE.

@@

FE-based tests results are prensented in Table \ref{NullTestTable}. Individual level data are used thanks to the panel structure of both surveys. Since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE. Also,the regresions are adjusted accordingly depending on the quarterly and monthly frequency of SPF and SCE. Since these regressions are based on 1-year inflations in overlapping periods, white standard error is computed for hypothesis testing.

@@

The second batch of tests in Table \ref{RevEfficency} focus on estimating forecasting efficiency using revisions of mean forecasts and uncertainty, hereafter referred as revision-based tests.  In plain words, the revision from 1-year-ahead forecast to nowcast of current-year inflation is efficient according two criteria (1) Forecast revision does not depend on past information, including the past revisions. (2) Drop in uncertainy is sufficiently rapid to reflect the uncertainty of all realized shocks.

The mean revision test by \citet{fuhrer2018intrinsic} takes the following form (using 1 period as an example):

@@

In the above equation $\beta =0$ according to FIRE, because rational forecast revision only responds to newly realized shocks thus it is not predictable by past revisions.\footnote{Adding $y_{t+1|t}$ to both sides of Equation \ref{RevEffMeanTest} gives an equivalent null hypothesis used by \citet{fuhrer2018intrinsic}: coefficient of regression of $y_{t+1|t+1}$ on  $y_{t+1|t}$ is $1-\beta=1$. }. Since we have four vintages of the forecasts from SPF, the above specification can include lagged revisions up to 4 quarters.

The test with uncertainy simply replaces the revision of forecast with revision in uncertainty $\sigma^2_{i,t+1|t+1} - \sigma^2_{i.t+1|t}$, for instance. This regresion follows from Equation \ref{VarSERv} for SE and Equation \ref{VarNIRv} for NI. Although it  cannot be directly used as a test against FIRE null, the autocorrelation coefficient speaks to the speed of drop in uncertainty. Depending on the model, one can interprete it as the particular structural parameter of rigidty, as shown in Figure \ref{rigidity}.

Top panel in Table \ref{RevEffMeanTest} and bottom panel presents the results for mean forecast. Following \citet{fuhrer2018intrinsic}, I include median forecast available at time $t$ and $t-1$ as an indicator of past information for the revision regression. In the first column of each panel, I report the regression on a constant.

What's surprising is the mean revision in forecast being negative and significant. Forecaters on average make downward adjustment of 1.26 percentage points of CPI and  1.1 perentage points of PCE from her previous year forecast of the same-period inflation.

The second to fourth columns of each panel in Table \ref{RevEfficency} checks auto correlation of revisions including different lags. Revisions of forecasts are serially correlated over 4 quarters and the coefficients are all positive and significant. Also, the median forecasts as the past information always predicts a negative revision with significant coefficients. This is evidence against null hypothesis of FIRE and my estiamtes are comparable with those by \citet{fuhrer2018intrinsic}.

In the bottom panel reports auto regression results for revision in uncertainty. Again, the first column first test the mean revision against the null being zero. The mean revisions in uncertainty are both negative(0.5-0.6 percentage poitns equivalence in standard devation of uncertainty) and statistically sigificant, confirming our observation from Figure \ref{RevisionHist} that forecaters are more certain about current inflation compared her previous year forecast.

The second to fourth column rejects the null of non-serial correlation for both CPI and PCE forecasts. The revision to CPI seems more efficient as serial correlation is with only one quarter lag. For PCE, the revisions in uncertainty are serially correlated with all past three quarters.

@@

Table \ref{WeakRevEfficiency} presents the results with the revision replaced with change in mean forecasts and uncertainty, i.e. $y_{t|t-1}$ to $y_{t+1|t}$. The auto-correlation of change in mean forecast and uncertainty does embed  tests of null of FIRE (Equation \ref{VarREPop}). But if the individual forecasts and their uncertainty turn out to be persisent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.

@@

In Figure \ref{Inflationshocks}, all four shocks are plotted in quarterly between 1985-2019. All shocks are normalized by its respective sample standard deviations.

@@

The primary focus of this paper is the behavior of uncertainty. Its responses to the absolute value of various shocks is presented in the bottom of the panel. Since  average uncertainty do not directly depend on the realizations and sizes of the shocks in various models, as shown in Equation \ref{VarREEq}  Equation \ref{VarSEPop}, and Equation \ref{VarNIEq}, the response of uncertainty cannot be used as a screening device of  FIRE and rigidity models. Instead, it should be taken as a basic consistency check of different theories with respect to the behavior of uncertainty.
